Blueprint for efficient nuclear spin characterization in color center

### 2024-02-07 article.tex
ok

\section*{Acknowledgments}
We acknowledge financial support by European Union's Horizon 2020 research and innovation program ASTERIQS under grant No. 820394, European Research Council advanced grant No. 742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, the DFG (FOR 2724), the Max Planck Society, and the Volkswagentiftung. M.Z. thanks Max Planck School of Photonics for financial support.

>>>>

\section*{Acknowledgments}
We acknowledge financial support by European Union's Horizon 2020 research and innovation program ASTERIQS under grant No. 820394, European Research Council advanced grant No. 742610, SMel, Federal Ministry of Education and Research (BMBF) project MiLiQuant and Quamapolis, Spinning and QR.X the DFG (FOR 2724,INST 41/1109-1 FUGG), the Max Planck Society, and the Volkswagentiftung. M.Z. thanks Max Planck School of Photonics for financial support.
